Ms 1

### 2017-11-08 ms1/ms1_display.Rmd
display: new no refills

```{r pop_chars}
pop_chars = read_tsv('tables/pop_chars.tsv') %>%
  select(-sem_age, -sem_n_cc) %>%
  mutate_at(vars(n_female:n_region_midwest), function(x) x / .$n_bene * 100)

@@

```{r pde_counts}
read_tsv('raw_data/firstfill.tsv') %>%
  group_by(firstfill) %>%
  summarize(n_pde=sum(n_pde)) %>%
  #arrange(desc(firstfill)) %>%
  mutate(cum_n=prettyNum(cumsum(n_pde), big.mark=',')) %>%
  kable(caption='PDEs by firstfill (or refill)')
```

@@

claims_by_abx %>%
  filter(abx=='overall') %>%
  ggplot(aes(x=year, y=cpkp)) +
  geom_point() + geom_line() +
  scale_y_continuous(limits=c(975, 1525), breaks=c(1000, 1125, 1250, 1375, 1500)) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, all abx')

@@

## Trends in appropriateness

@@

# fraction inappropriate in 2011
risk_ratio_f = function(or, p) or / (1 + p * (or - 1))
f_i = scan('tables/inapprop_risk_2011.txt')

```{r drug_trends_display}
drug_trends %>%
  select(abx, y, ymin, ymax) %>%
  mutate_if(is.numeric, function(x) format(x, digits=2, nsmall=2)) %>%
  kable(caption='Drug trends: Percent change from 2011 to 2014')

abx_trends_levels = drug_trends %>%
  filter(abx != 'overall') %$%
  { c('overall', 'overall_app', 'overall_inapp', rev(abx)) }

drug_and_inapprop_trends = drug_trends %>%
  select(abx, y, ymin, ymax) %>%
  bind_rows(inapprop_trends) %>%
  mutate(abx=factor(abx, levels=rev(abx_trends_levels)))

drug_and_inapprop_trends %>%
  ggplot(aes(x=abx, y=y, ymin=ymin, ymax=ymax)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))

drug_and_inapprop_trends %>%
  arrange(desc(abx)) %>%
  kable(caption='Percent changes; same data as in figure')
```

@@

```{r prescribing_practice}
dx_counts_2011 = read_tsv('raw_data/dx_counts.tsv') %>%
  left_join(select(pop_chars, year, n_bene), by='year') %>%
  mutate(dkpy=round(n_encounter/n_bene*1000)) %>%
  filter(year==2011) %>%
  select(dx_cat, dkpy)

dx_from_pde_2011 = read_tsv('raw_data/dx_from_pde.tsv') %>%
  filter(year==2011) %>%
  mutate(f_with_dx=n_pde_with_encounter/n_pde_with_any_encounter) %>%
  select(antibiotic, dx_cat, year, f_with_dx)

dx_to_pde_table = read_tsv('tables/dx_to_pde_table.tsv') %>%
  select(-n_encounters) %>%
  filter(year %in% c(2011, 2014)) %>%
  gather('abx', 'f_with_abx', azithromycin:clindamycin)

# swo: convert ORs to RRs!
rr2pct = function(x) (x - 1) * 100

@@

```{r combined_table}
format2 = function(x) format(round(x, 2), digits=2, nsmall=2)

part1 = dx_counts_2011 %>%
  mutate(dkpy=as.character(dkpy)) %>%
  spread(dx_cat, dkpy) %>%
  mutate(abx='dx', key1='dkpy', key2='')

part2 = dx_from_pde_2011 %>%
  # throw out some rare drugs
  filter(!is.na(dx_cat)) %>%
  mutate(f_with_dx=format2(f_with_dx*100)) %>%
  spread(dx_cat, f_with_dx) %>%
  mutate(key1='pde2dx', key2=as.character(year)) %>% rename(abx=antibiotic)

part3 = dx_to_pde_table %>%
  mutate(f_with_abx=format2(f_with_abx*100)) %>%
  spread(dx_cat, f_with_abx) %>%
  mutate(key1='dx2pde', key2=as.character(year))

part4 = dx_to_pde_trends %>%
  spread(dx_cat, change) %>%
  mutate(key1='dx2pde_trend', key2='')

combined_table = bind_rows(part1, part2, part3, part4) %>%
  mutate(abx=factor(abx, levels=c('dx', abx_levels)),
         key1=factor(key1, levels=c('dkpy', 'pde2dx', 'dx2pde', 'dx2pde_trend'))) %>%
  arrange(abx, key1, key2)
```

@@

```{r respiratory}
combined_table %>%
  select(abx, key1, key2, pneumonia, sinusitis, uri, bronchitis) %>%
  filter(abx %in% c('dx', 'azithromycin', 'levofloxacin', 'amoxclav')) %>%
  kable
```

@@

```{r other_respiratory}
combined_table %>%
  select(abx, key1, key2, pharyngitis, asthma, other_resp) %>%
  filter(abx %in% c('dx', 'azithromycin', 'levofloxacin', 'amoxclav')) %>%
  kable
```

@@

```{r uti}
combined_table %>%
  select(abx, key1, key2, uti, uti_t3) %>%
  filter(abx %in% c('dx', 'ciprofloxacin', 'tmpsmx', 'nitrofurantoin')) %>%
  kable
```

@@

```{r ssti}
combined_table %>%
  select(abx, key1, key2, ssti, ssti_t3) %>%
  filter(abx %in% c('dx', 'cephalexin', 'tmpsmx', 'clindamycin')) %>%
  kable
```

>>>>

```{r pop_chars}
pop_chars = read_tsv('tables/pop_chars.tsv') %>%
  mutate_at(vars(n_female:n_region_midwest), function(x) x / .$n_bene * 100)

@@

```{r claims_by_fill}
claims_by_fill = read_tsv('tables/claims_by_fill.tsv') %>%
  mutate(f_refill=refills/overall_wrefill)

claims_by_fill %>%
  kable(caption='PDEs by refill')

#  mutate(cum_n=prettyNum(cumsum(n_pde), big.mark=',')) %>%
```

@@

claims_by_abx %>%
  filter(abx %in% c('overall', 'overall_approp', 'overall_inapprop')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_point() + geom_line() +
  #scale_y_continuous(limits=c(0, 1525), breaks=c(1000, 1125, 1250, 1375, 1500)) +
  scale_y_continuous(limits=c(0, 1525), breaks=c(0, 250, 500, 750, 1000, 1250, 1500)) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, all abx')

@@

@@

```{r drug_trends_display}
format_p = function(p) {
  if_else(p < 0.001, '< 0.001', as.character(round(p, 3)))
}

drug_trends %>%
  filter(abx != 'overall_wrefill') %>%
  mutate(adj.p=p.adjust(p.value, method='BH')) %>%
  select(abx, y, ymin, ymax, p.value) %>%
  mutate_at(vars(y, ymin, ymax), function(x) format(x, digits=2, nsmall=2)) %>%
  mutate(p.value=format_p(p.value)) %>%
  kable(caption='Drug trends: Percent change from 2011 to 2014')

drug_trends %>%
  filter(abx != 'overall_wrefill') %>%
  # put the abx in order
  arrange(desc(y)) %>%
  mutate(abx=fct_inorder(factor(abx))) %>%
  mutate(abx=fct_relevel(abx, c('overall', 'overall_inapprop', 'overall_approp'))) %>%
  mutate(abx=fct_rev(abx)) %>%
  # plot
  ggplot(aes(x=abx, y=y, ymin=ymin, ymax=ymax)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32.5), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

@@

```{r prescribing_practice}
dx_to_pde_table = read_tsv('tables/dx_to_pde_table.tsv') %>%
  select(-n_encounters) %>%
  filter(year %in% c(2011, 2014)) %>%
  gather('abx', 'f_with_abx', azithromycin:clindamycin)

# swo: convert ORs to RRs!
risk_ratio_f = function(or, p) or / (1 + p * (or - 1))
rr2pct = function(x) (x - 1) * 100

@@

```{r combined_table}
format_pct = function(x) format(round(x*100, 2), digits=2, nsmall=2)

combined_table = dx_to_pde_table %>%
  mutate(f_with_abx=format_pct(f_with_abx)) %>%
  spread(year, f_with_abx) %>%
  left_join(dx_to_pde_trends, by=c('dx_cat', 'abx')) %>%
  arrange(abx, dx_cat)
```

@@

```{r respiratory}
combined_table %>%
  filter(dx_cat %in% c('pneumonia', 'sinusitis', 'uri', 'bronchitis'),
         abx %in% c('dx', 'azithromycin', 'levofloxacin', 'amoxclav')) %>%
  kable
```

@@

```{r other_respiratory}
combined_table %>%
  filter(dx_cat %in% c('pharyngitis', 'asthma', 'other_resp'),
         abx %in% c('azithromycin', 'levofloxacin', 'amoxclav')) %>%
  kable
```

@@

```{r uti}
combined_table %>%
  filter(dx_cat %in% c('uti', 'uti_t3'),
         abx %in% c('dx', 'ciprofloxacin', 'tmpsmx', 'nitrofurantoin')) %>%
  kable
```

@@

```{r ssti}
combined_table %>%
  filter(dx_cat %in% c('ssti', 'ssti_t3'),
         abx %in% c('dx', 'cephalexin', 'tmpsmx', 'clindamycin')) %>%
  kable
```

## Projected appropriateness trend

# fraction inappropriate in 2011
f_i = scan('tables/inapprop_risk_2011.txt')
